\bf Model Visualization Techniques for a Social Network Model

### 2017-06-03 paper.Rnw
notation

When node $i$ is given the chance to change a tie, \hh{`we assume that they wish' sounds strange - don't assume wishes, state assumptions} we assume that they wish to maximize the value of their objective function $f_i(\boldsymbol{\beta}, x)$ plus a random element, $U_i(x)$, where the $U_i(x)$ are from \hh{XXX don't cite here - just state that Snijder suggest the use of a type 1 extreme value distribution on top of the objective function. XX What is the thought behind that? } ``the type 1 extreme value distribution (or Gumbel distribution) with mean 0 and scale parameter 1" \citep[p. 368]{snijders01}. This distribution, which is also known as the log-Weibull distribution, has probability distribution function, using $\mu$ for the mean parameter and $\sigma$ for the scale parameter, of

@@

Using this distribution is convenient because it allows the probablity the actor $i$ chooses to change its tie to actor $j$ in terms of the objective function alone. Let $p_{ij}(\boldsymbol{\beta}, x)$ be this probability. Next, write the network $x$ in its potential future state, where the tie $x_{ij}$ has changed to $1-x_{ij}$, as $x(i \leadsto j)$. Then, the probility that the tie $x_{ij}$ changes is

>>>>

When node $i$ is given the chance to change a tie, \hh{`we assume that they wish' sounds strange - don't assume wishes, state assumptions} we assume that they wish to maximize the value of their objective function $f_i(\boldsymbol{\beta}, x)$ plus a random element, $U_i(x)$, where the $U_i(x)$ are from \hh{XXX don't quote here - just state that Snijder suggest the use of a type 1 extreme value distribution on top of the objective function. XX What is the thought behind that? } ``the type 1 extreme value distribution (or Gumbel distribution) with mean 0 and scale parameter 1" \citep[p. 368]{snijders01}. This distribution, which is also known as the log-Weibull distribution, has probability distribution function, using $\mu$ for the mean parameter and $\sigma$ for the scale parameter, of

@@

Using this distribution \hh{XXX I'm not following - which distribution do you mean by `this' distribution? The density above is the type 1 extreme value density. I got lost at the  ``objective function $f_i(\boldsymbol{\beta}, x)$ plus a random element, $U_i(x)$"} is convenient because it allows the probability the actor $i$ chooses to change its tie to actor $j$ in terms of the objective function alone. Let $p_{ij}(\boldsymbol{\beta}, x)$ be this probability. Next, write the network $x$ in its potential future state, where the tie $x_{ij}$ has changed to $1-x_{ij}$, as $x(i \leadsto j)$. Then, the probility that the tie $x_{ij}$ changes is
